Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2022-05-02 Proposal/ch-abm.tex
Move proposal to subfolder.

As their collective task, agents seek an optimal point on a rugged fitness landscape.
This landscape is generated using the NK model \cite{kauffman_towards_1987, weinberger_local_1991} (see Appendix \ref{apx-nk}).
The NK model is a ``tuanbly rugged'' objective function parameterized by two variables:
the number of bits in the input string ($N$),
and the number bits used to compute each contribution to the objective function ($K+1$).
These parameters can be used to tune problem size and complexity, respectively.
The resulting objective function maps $N$-bit strings to real numbers in $[0,1]$.

@@

We use an agent-based simualation to model deliberation between individuals.
We model communication between agents using a time-dependent network $(V,E_t)$.
The vertices $V$ correspond to the agents (individuals).
The edges $E_t$ allow agents to exchange information with their immediate neighbors at time $t$.
Over the course of the simulation, agents seek to maximize some objective function $Q(s)$.
We use binary strings of length $d$ as our solution space: $s \in \mathbb{Z}^d$.
We generate the objective function $Q(s)$ using the NK model \cite{kauffman_towards_1987, weinberger_local_1991} (see Appendix \ref{apx-nk}).

>>>>

As their collective task, agents seek an optimal point on a rugged fitness landscape.
This landscape is generated using the NK model \cite{kauffman_towards_1987, weinberger_local_1991} (see Appendix \ref{apx:nk}).
The NK model is a ``tuanbly rugged'' objective function parameterized by two variables:
the number of bits in the input string ($N$),
and the number bits used to compute each contribution to the objective function ($K+1$).
These parameters can be used to tune problem size and complexity, respectively.
The resulting objective function maps $N$-bit strings to real numbers in $[0,1]$.

@@

We use an agent-based simualation to model deliberation between individuals.
We model communication between agents using a time-dependent network $(V,E_t)$.
The vertices $V$ correspond to the agents (individuals).
The edges $E_t$ allow agents to exchange information with their immediate neighbors at time $t$.
Over the course of the simulation, agents seek to maximize some objective function $Q(s)$.
We use binary strings of length $d$ as our solution space: $s \in \mathbb{Z}^d$.
We generate the objective function $Q(s)$ using the NK model \cite{kauffman_towards_1987, weinberger_local_1991} (see Appendix \ref{apx:nk}).
